Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-06-21 Paper/gammaRays.tex
Changed 3 to 4 observations in Introduction

	Most of the bursts in the catalog, however, do not have enough events with over $\unit[1]{GeV}$ energies to do desired computations, so we choose only those bursts, from which at least $10$ photons were detected in the high energy band.
	This leaves $3$ of them: 080916C \cite{Tajima:2009az}, 090902B \cite{Abdo:2009pg} and 090926A \cite{Bregeon:2011bu}.

	For these 3 bursts we compute both high and low energy distributions of photon times.
	We subtract the low energy background estimate from the low energy CDF, and add the high energy background estimate to it.
	This makes the low energy CDF non-monotonous and, rigorously speaking, we cannot use the 2-sample Kolmogorov-Smirnov test on it.
	However, since there is a much greater number of photons on lower energies, we can think of the low energy CDF as continuous.
	Therefore, this non-monotonicity will be negligible, and will not harm the KS-test results much.

>>>>

	Most of the bursts in the catalog, however, do not have enough events with over $\unit[1]{GeV}$ energies to do desired computations, so we choose only those bursts, from which at least $10$ photons were detected in the high energy band.
	It leaves $4$ of them: 080916C \cite{Tajima:2009az}, 090510 \cite{Ackermann:2010us}, 090902B \cite{Abdo:2009pg} and 090926A \cite{Bregeon:2011bu}.

	For these 4 bursts we compute both high and low energy distributions of photon times, and subtract the background estimates from them.
	This makes CDFs non-monotonous and, rigorously speaking, we cannot use the 2-sample Kolmogorov-Smirnov test on it.
	However, since the number of photons is much higher than estimated background, this non-monotonicity will be negligible, and will not harm the KS-test results much.
